A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-08-11 docs/data_v1.01.tex
Wrote sections on MGE fitting results.
Added stuff to data section.

\section{Data}

@@

\begin{itemize}
\item Hubble Space teleskope (HST) imaging by \cite{SWELLSI} in two filters (F450W amd F814W)
\item I filter: for surface brightness distribution of J1331's bulge for Jeans modelling
\item ??? filter: to identify bluish lensing images
\end{itemize}

>>>>

\section{Data} \label{sec:data}

@@

\begin{itemize}
\item Hubble Space teleskope (HST) imaging by \cite{SWELLSI} in two filters (F450W amd F814W)
\item I filter: for surface brightness distribution of J1331's bulge for Jeans modelling
\item ??? filter: to identify bluish lensing images
\item drizzled image
\end{itemize}

\paragraph{Stellar Kinematics.} We use the stellar kinematics for J1331 measured by [TO DO: REF: Dutton 2013]. They obtained long-slit spectra along J1331's major-axis with the Low Resolution Imaging Spectrograph (LRIS) on the Keck I 10m telescope. The width of the slot was 1 arcsec and the seeing Conditions had a FWHM of $\sim 1.1$ arcsec. Spectra for spatial bins of different widths along the major axis were extracted. Analogously to [TO DO: REF: Dutton 2011] they measured line-of-sight rotation velocities ($v_\text{rot}$) and stellar velocity dispersion ($\sigma$) by fitting Gaussian line profiles to emission lines in these spectra. Gas kinematics were extracted from fits to H$\alpha$ and NII lines, as tracers for inonized gas.
\\The stellar kinematics, $v_\text{rot}$, $\sigma$ and $v_\text{rms}^2=v_\text{rot}^2 + \sigma^2$ are [TO DO]
